Naive Bayes Classifier

### 2019-02-26 NB_2r2c.Rmd
update

This block is an alternative method to get the same data tables out using ```tidy``` format. It seems much less direct, but may be over-written.
```{r tidy_prediction_table}

@@

#Tabular and Graphical Comparisons of Coded and Predicted Categories
These code blocks compare the hand-coded versus NB-predicted frequencies. There are separate comparisons for the Subject and Structure categories, and both tabular and graphical comparisons.

>>>>

This block is an **alternative method** to get the same data tables out using ```tidy``` format. It seems much less direct, but may be over-written.
```{r tidy_prediction_table}

@@

#Comparing Coded and Predicted Categories
These code blocks compare the hand-coded versus NB-predicted frequencies. There are separate comparisons for the Subject and Structure categories, and both tabular and graphical comparisons.
